### 2024-02-19 paper_sisc_first_revision/localpsf.tex
about to do one last read before sending to Omar

We use the proposed method to approximate the Newton (or Gauss-Newton) Hessians
in inverse problems governed by PDEs which model steady state ice
sheet flow~\cite{PetraEtAl12} (Section~\ref{sec:ice}) and advective-diffusive transport of a contaminant~\cite{PetraStadler11}
(Section~\ref{sec:adv}). These inverse problems are described in detail in their respective sections.
In both cases, to reconstruct the unknown parameter fields, denoted $q$, the inverse problems are formulated as nonlinear least squares
optimization problems, whose objective functions consist of a data misfit term
(between the observations and model output) and a bi-Laplacian
regularization term following~\cite{VillaPetraGhattas21}. The
regularization is centered at a constant function $q_0(x)$. To
mitigate boundary effects
%For stokes q_0(x) = 10.5$%
we use a constant coefficient Robin boundary condition as
in~\cite{Roininen14}. The parameters for the bi-Laplacian operator are chosen
so that the Green's function of the Hessian of the regularization has
a characteristic length of $0.25$ of the domain radius. For the
specific setup, we refer the reader to~\cite[Section
  2.2]{VillaPetraGhattas21}. In all numerical results we choose the
regularization parameter (which controls the overall strength of the regularization) using the Morozov discrepancy
principle~\cite{Vogel02}.

>>>>

We use the proposed method to approximate the integral kernel in a blur problem (Section~\ref{sec:frog}), and the Newton (or Gauss-Newton) Hessians
in inverse problems governed by PDEs which model steady state ice
sheet flow~\cite{PetraEtAl12} (Section~\ref{sec:ice}) and advective-diffusive transport of a contaminant~\cite{PetraStadler11}
(Section~\ref{sec:adv}). These inverse problems are described in detail in their respective sections.
In both inverse problems, to reconstruct the unknown parameter fields, denoted $q$, the inverse problems are formulated as nonlinear least squares
optimization problems, whose objective functions consist of a data misfit term
(between the observations and model output) and a bi-Laplacian
regularization term following~\cite{VillaPetraGhattas21}. The
regularization is centered at a constant function $q_0(x)$. To
mitigate boundary effects
%For stokes q_0(x) = 10.5$%
we use a constant coefficient Robin boundary condition as
in~\cite{Roininen14}. The parameters for the bi-Laplacian operator are chosen
so that the Green's function of the Hessian of the regularization has
a characteristic length of $0.25$ of the domain radius. For the
specific setup, we refer the reader to~\cite[Section
  2.2]{VillaPetraGhattas21}. In all numerical results we choose the
regularization parameter (which controls the overall strength of the regularization) using the Morozov discrepancy
principle~\cite{Vogel02}.
